Developing Software Center Using Evolutionary Prototyping Based-on HTML5

### 2014-05-02 Latex/Paper_format.tex
add desain n UML

\section{Introduction}
% no \IEEEPARstart
Software Center is software to manage application in a operating system such as install, delete or upgrade applications. It is a required software in all operating system, both conventional or mobile devices. BlankOn as the Indonesian local operating system should have this application but in reality this application is not yet available [1].

Traditionally, to do package management, user deal with installing package form console with apt syntac. This way is worst to other people. In other way user can use Synaptic Package Manager, a simple software center. But this interface just to old style.

HTML5 is a trend of programming because this technology easy to adapted, can run in multple platfrom up to desktop utilization [2].

This research tries to make software center HMTL5-based as solution for BlankOn.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
\section{Software Center}

YaST (yet another setup tool)
Software center for opensuse. It use to manage all of user need for use opensuse. Example to install application, package, network setting etc. YaST devel form ruby and YCP and qt for UI, base c++[3 yast vendor].

scr uset to injek scrip. interface base on qt.

Ubuntu Software Center
Software manajemen for ubuntu by canonical. It is free software written in Python, PyGTK/PyGObject based on GTK+ and the further development of the GNOME application, gnome-app-install. base commant for apt manajemen.[4][5]

@@

\subsection{Webkit}
webkit is renderin page to run html5, it base bla
figure 1 how webkit work

\subsection{WarSi}
WarSi (Warung aplikasi)
gui from apt command
how it work.
firgure 2.

\section{Development WarSi}
\subsection{Development Method}
Developmen use evoluitionary protoyiping,
- because (alasan) [7]
figure 3 how prototyping

\subsubsection{Initial Consep and requirment}
what konsep

@@

\subsection{UML (Unified Modele Language}

\subsubsection{Use Case Diagram}
as figure 4
thi app have 2 main requrment

\subsubsection{Activity Diagram}
- a
- b

@@

\subsection{Result Develop}

@@

>>>>

\section{Introduction}
% no \IEEEPARstart
Software Center has a function to management software, which adds, removes and update software. Its existence is necessary in all operating systems both desktop and mobile devices. This application use on OpenSUSE, Ubuntu, Mac OS X, Android, iOS, BlackBerry and Windows. However, these applications are not in BlankOn Linux as Indonesian local Linux distribution. Installation of applications in BlankOn Linux currently can be done in the traditional way: first from the console (terminal), thi way can be done if you know the name of the application you want to install the package. The second way to use the Synaptic Package Manager a management application packages. Despite using a GUI (graphic user interface) but still only be done if you know the name of the application you want to install the package and limited its use. Making it difficult for an ordinary user to install the application.

Similar applications that have been there is the Ubuntu Software Center for Ubuntu distribution. This application allowing licensed OpenSource applied to BlankOn Linux. However, since these applications have become a trademark of Ubuntu, needs further modification process. This process takes time and is not guaranteed to run well so, what ideas arise if made ​​to start from scratch.

HTML5 is a trend of programming because this technology easy to adapted, can run in many platforms up to desktop utilization [2]. Manokwari Desktop a desktop environment for BlankOn Linux is base on HTML5. Development software center base on HTML5 can run consistent with development of BlankOn Linux [3]. This research tries to make software center HMTL5-based as solution for BlankOn Linux.

% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
\section{Similar Software Center}

YaST (Yet another Setup Tool)
Software center for openSUSE. It use to manage all of user need for use openSUSE. Example to install application, package, network setting etc. YaST use ruby and YCP for language programming and Qt for user interface[3].

Ubuntu Software Center
Software management for Ubuntu by Canonical. It is free software written in Python, PyGTK/PyGObject based on GTK+ and the further development of the GNOME application, gnome-app-install.[4][5]

@@

\subsection{Webkit and WebkitGTK+}
WebKit is a layout engine software component for rendering web pages in web browsers. It powers Apple's Safari web browser and was previously used in Google's Chrome web browser. Figure 1 and 2 shows how Webkit work.

WebKit is also used as the basis for the experimental browser included with the Amazon Kindle e-book reader, as well as the default browser in the Apple iOS, Android, BlackBerry 10, and Tizen mobile operating systems. WebKit's C++ application programming interface provides a set of classes to display web content in windows, and implements browser features such as following links when clicked by the user, managing a back-forward list, and managing a history of pages recently visited.[6] bart

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{image/webkit.png}
\caption{How Webkit Work}
\end{figure}

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{image/webkitcomponents.png}
\caption{Webkit Major Components}
\end{figure}

WebKitGTK+ is the GNOME platform port of the WebKit rendering engine. Offering WebKit’s full functionality through a set of GObject-based APIs, it is suitable for projects requiring any kind of web integration, from hybrid HTML/CSS applications to full-fledged web browsers, like Epiphany and Midori. It’s useful in a wide range of systems from desktop computers to embedded systems like phones, tablets, and televisions. WebKitGTK+ is made by a lively community of developers and designers, who hope to bring the web platform to everyone.[7] webkitgtk.org

\subsection{WarSi}
WarSi (Warung aplikasi)
gui from apt command

\section{Development WarSi}
\subsection{Design System}
Figure 3 show how design of WarSi.

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{image/DesignSystem.png}
\caption{Design System}
\end{figure}

\subsection{Development Method}
System development methods used in this study is the method of Evolutionary Prototyping. Evolutionary prototyping method has the steps as shown in Figure 3.

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{image/ep-model.png}
\caption{Evolutionary Prototyping Process Model}
\end{figure}

Evolutionary prototyping provides other benefits including:
\begin{itemize}
\item the clarification of management and user requirements;
\item the ability to uncover missing or previously unknown requirements;
\item the flexibility to meet changing constraints for software systems;
\item the provision of a method whereby users, management, and developers can communicate about systems;
\item the easing of maintenance tasks;
\item the creation of ‘better’ user interfaces;
\item prototyping with quality; and
\item the ability for developers to reflect on lessons learned during system development.
\end{itemize}

Step of Evolutionary Prototyping:
\subsubsection{Initial Consep and requirment}
what konsep

@@

\subsection{UML (Unified Modeling Language}

\subsubsection{Use Case Diagram}
Figure 4 show the use case diagram for software center.

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.7]{image/Usecase.png}
\caption{Use case Diagram}
\end{figure}

This is a description of the process in the use case diagram:
\begin{itemize}
\item Search Application\\
This process is performed to find the application as the user desires. Once the search is complete the user can install / remove applications and application upgrades.
\item Repository Management\\
This funtions make user can change source repository, save, update and upgrade system.
\end{itemize}

\subsubsection{Activity Diagram}
Figure 5 show activity diagram generaly.

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.7]{image/ActivityDiagram.png}
\caption{Activity Diagram}
\end{figure}

Activity Diagram Search Applications

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{image/ADSearchApp.png}
\caption{Activity Diagram Search Application}
\end{figure}

Figure 6 is an activity diagram for a search application. Search Application is divided into two, namely by entering a keyword in the search field and the search for applications by category. Process for Figure 6 are:

\begin{itemize}
\item Users select search for applications by name or by category of applications,
\item If you select by name, users enter a keyword or the name of the application you are looking for in the search field to find the application,
\item If you select a category based application, the user selects a category that existed until the application is found,
\item Application is found, the user chooses to install/remove or update the application,
\item Installation process, and the process is complete.
\end{itemize}

Activity Diagram Repository Management

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{image/ADManagement.png}
\caption{Activity Diagram Repository Management}
\end{figure}

Process for Figure 7 are:
\begin{itemize}
\item User select a menu from the main menu next repository, system will display the page repository, there are two options, choose source repository or directly perform the update,
\item User can make changes to the repository by selecting the list
repository that is already available,
\item When the user makes changes to the repository, the system will saved the changes,
\item When the user performs an update to the update repository the repository will be made and the system will display the process update,
\item After update user can upgrade system if available, then the system will display the process upgrade.
\item Process is completed.
\end{itemize}

@@

\subsection{Result Development}

@@

\bibitem{IEEEhowto:kopka}
Carter, Ryan A.,Antón, Annie I.,Dagnino, Aldo., Williams, Laurie, \emph{Evolving Beyond Requirements Creep:A Risk-Based Evolutionary Prototyping Model}, North Carolina State University, 2001.
